add commits in my local repository
long time ago, I made a commit in my local repository. I want to add more commits to it. How can I do that?
To add more commits to your local repository, you can follow these steps:
1. Make changes to your files in your local repository using your preferred text editor or IDE.
2. Use the command `git add <file_name>` to stage the changes for commit.
3. Use the command `git commit -m "Your commit message"` to commit the changes with a descriptive message.
4. Repeat steps 1-3 for each set of changes you want to commit.
5. Once you have made all your commits, you can use the command `git log` to view the commit history and verify that your new commits have been added to the local repository.
6. If you want to push your commits to a remote repository, use the command `git push origin <branch_name>` to push your committed changes to the remote repository on GitHub.
7. If you want to create a new branch for your commits, use the command `git branch <branch_name>` to create a new branch and `git checkout <branch_name>` to switch to that branch before making your commits.
8. If you want to merge your commits from a branch back into the main branch, use the command `git checkout main` to switch to the main branch and then use `git merge <branch_name>` to merge the changes from your branch into the main branch.
9. If you encounter any merge conflicts during the merge process, resolve them by editing the conflicting files, staging the resolved files with `git add`, and committing the changes with `git commit`.
10. Finally, use `git push origin main` to push the merged changes to the remote repository on GitHub.